---
output: 
  html_document:
    keep_md: true
title: "gvsu215"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gvsu215

<!-- badges: start -->
<!-- badges: end -->

`gvsu215` contains a series of wrapper functions around select `{mosaic}` and `{ggformula}` functions, with help from `{flextable}`. The goal is to provide introductory statistics students/learners with an easy way to generate nice-looking plots and tables without focusing on the code used to create them. All tables and plots generated from this package have been doctored and have had themes pre-applied. As such, output will not print in "messy" format to the R console and can be used interactively, including in R Markdown documents.

This package was designed and tailored for Grand Valley State University (course code: STA 215) but can be used by anyone.

## Installation

You can install the development version of gvsu215 from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ian-curtis/gvsu215")
```

## Prerequisites

In order to use this package, you will need a basic understanding of R syntax and how to run a function in your preferred working environment. Functions use formula syntax (e.g., `var1 ~ var2`) and thus knowledge of formulas is needed as well.

## Examples

This package is best used for creating simple plots and charts where extensive customization is not necessary. For instance, you may just want to see summary statistics.

```{r num-sum, message = FALSE}
library(gvsu215)

num_sum(mtcars, ~wt, na_rm = TRUE)
```

Or maybe you just need percentiles:

```{r pctile}
pctile(mtcars, ~wt, probs = c(0, .25, .4, .5, .6, .75, 1))
```

There is also support for a variety of plots...

```{r plots, out.width = "50%"}
plot_bar(mtcars, ~cyl, type = "percent")

plot_box(mtcars, wt~gear, fill = 'orangered4', x = "Gear", y = "Weight", title = "Boxplot of Weight by Gear")

plot_scatter(mtcars, wt~drat)
```

... and statistical inference.

```{r inference}
infer_prop1(mtcars, ~vs, success = 1)

infer_paired(mtcars, var1 = ~drat, var2 = ~wt)

infer_mean2_int(mtcars, wt~vs)

suppressWarnings(infer_chisq(mtcars, cyl~gear))
suppressWarnings(infer_chisq(mtcars, cyl~gear, type = "expected"))

infer_anova(mtcars, cyl~gear, digits = 2)
```

# Help, Bug Reports, and Feature Requests

Errors happen! If you come across an error you don't think you should have, feel free to [create an issue on GitHub](https://github.com/ian-curtis/gvsu215/issues). If you'd like to suggest a change or addition, you can use the issues page for that, too!


