---
title: "Cheatsheet"
subtitle: "Designed For GVSU STA 215 Students"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cheat Sheet}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

There are many functions contained in this package and it can get annoying to have to keep checking documentation. The purpose of this article is to provide templates for the basic features of each function. That way, you can simply copy the template and edit where need be.

# Installation and Preparations

This package comes pre-installed on the GVSU Posit Workbench. All you need to do is load the package to access its functions.

```{r setup}
library(gvsu215)
```


Note: The Software Investigation starter program will always include a code chunk that loads the `gvsu215` package that includes the functions we need for STA215.

# Templates

The package's functions can be broken down into a few general categories: utilities, tables, plots, and inference. The templates below are broken up by GVSU's STA 215 textbook chapter and will include a generic example template. To evaluate, simply copy the code chunk (click on the copy icon that appears when you hover your mouse over the code chunk), double click on the "filler code" (the text in all capital letters and surrounded by underscores, `_EXAMPLE_`) and replace them with your respective code.

## Utilities

### Reading in Data

To read in data files, you will need to know the file path to the file. Then use

```{verbatim, lang = "r"}
_DATANAME_ <- read.csv("_FILEPATH_", header = TRUE)
```

Note: The Software Investigation starter program will include the code to read in the data.

### Subset Observations

```{verbatim, lang = "r"}
_NEWDATANAME_ <- _OLDDATANAME_ %>% 
  filter(_CONDITION_)
```

### Subset Variables

```{verbatim, lang = "r"}
_NEWDATANAME_ <- _OLDDATANAME_ %>% 
  select(_VARSTOKEEP_)
```

## Chapter 2: Categorical Data

### Frequency Table

```{verbatim, lang = "r"}
tbl_1var(_DATANAME_, ~_VARIABLE_)
```

### Bar Graph Using Percent

```{verbatim, lang = "r"}
plot_bar(_DATANAME_, ~_VARIABLE_, type = "percent", na_rm = FALSE)
```

Note: Change to `na_rm = TRUE` to eliminate missing values from plot.

### Bar Graph Using Counts

```{verbatim, lang = "r"}
plot_bar(_DATANAME_, ~_VARIABLE_, type = "count", na_rm = FALSE)
```

Note: Change to `na_rm = TRUE` to eliminate missing values from plot.

### Two-Way Table

```{verbatim, lang = "r"}
tbl_2var(_DATANAME_, _RESPONSE_~_EXPLANATORY_)
```

### Clustered Bar Graph

```{verbatim, lang = "r"}
plot_bar(_DATANAME_, ~_RESPONSE_, fill = ~_EXPLANATORY_, na_rm = FALSE)
```


## Chapter 3: One Quantitative

### Basic Numerical Summaries

```{verbatim, lang = "r"}
tbl_num_sum(_DATANAME_, ~_VARIABLE_, na_rm = TRUE)
```

### Percentile

```{verbatim, lang = "r"}
tbl_pctile(_DATANAME_, ~_VARIABLE_, probs = c(_PERCENTILES_))
```

Note: Replace percentiles with the values you want separated by commas.  For example, `c(0.80, 0.90, 0.95)`

### Boxplot

```{verbatim, lang = "r"}
plot_box(_DATANAME_, ~_VARIABLE_)
```

### Histogram

```{verbatim, lang = "r"}
plot_hist(_DATANAME_, ~_VARIABLE_)
```

Note: You can use `breaks` to control how many bars there are.

### Basic Numerical Summaries By Group

```{verbatim, lang = "r"}
tbl_num_sum(_DATANAME_, _RESPONSE_~_GROUPVARIABLE_, na_rm = TRUE)
```

### Percentiles By Group

```{verbatim, lang = "r"}
tbl_pctile(_DATANAME_, _RESPONSE_~_GROUPVARIABLE_)
```

### Boxplot By Group

```{verbatim, lang = "r"}
plot_box(_DATANAME_, _RESPONSE_~_GROUPVARIABLE_)
```

### Histogram By Group

```{verbatim, lang = "r"}
plot_hist(_DATANAME_, ~_VARIABLE_, group = ~_GROUPVARIABLE_)
```

Note: You can use `breaks` to control how many bars there are.

## Chapter 5: Estimation

Note: Confidence levels default to 95% but can be overridden with `conf_lvl = _DECIMAL_` (e.g., `conf_lvl = 0.9`). 

### Confidence Interval on $\mathrm{p}$

```{verbatim, lang = "r"}
infer_1prop_int(_DATANAME_, ~_VARIABLE_, success = "_SUCCESSCATEGORY_", conf_lvl = _CONFIDENCELEVEL_)
```

### Confidence Interval on &mu;

```{verbatim, lang = "r"}
infer_1mean_int(_DATANAME_, ~_VARIABLE_, conf_lvl = _CONFIDENCELEVEL_)
```

## Chapter 6: Two Quantitative

### Scatterplot

```{verbatim, lang = "r"}
plot_scatter(_DATANAME_, _RESPONSE_~_EXPLANATORY_, axis_lines = "none", ls_line = "hide")
```

Note: Change to `axis_lines = "both"` to grid the scatterplot.
Note: Change to `ls_line = "show"` to plot the regression line.

### Linear Correlation

```{verbatim, lang = "r"}
tbl_corr(_DATANAME_, _RESPONSE_~_EXPLANATORY_, na_rm = TRUE)
```

### Linear Regression

```{verbatim, lang = "r"}
infer_reg(_DATANAME_, _RESPONSE_~_EXPLANATORY_, reduced = "yes")
```

Note: Change to `reduced = "no"` to get test statistic and p-value.

### Scatterplot By Group

```{verbatim, lang = "r"}
plot_scatter(_DATANAME_, _RESPONSE_~_EXPLANATORY_, fill = ~_GROUPVARIABLE_, legend_title = "_LEGEND_")
```

## Chapter 7: Hypothesis Testing Introduction

### $\chi ^2$-Test

```{verbatim, lang = "r"}
# standard test
infer_chisq(_DATANAME_, _EXPLANATORY_~_RESPONSE_, type = "test")
```

```{verbatim, lang = "r"}
# expected counts
infer_chisq(_DATANAME_, _EXPLANATORY_~_RESPONSE_, type = "expected")
```

```{verbatim, lang = "r"}
# observed counts
infer_chisq(_DATANAME_, _EXPLANATORY_~_RESPONSE_, type = "observed")
```

### Confidence Interval for the Difference in Two Proportions

Note: Confidence levels default to 95% but can be overridden with `conf_lvl = _DECIMAL_` (e.g., `conf_lvl = 0.90`). 

```{verbatim, lang = "r"}
infer_2prop_int(_DATANAME_, _RESPONSE_~_EXPLANATORY_, success = _SUCCESSCATEGORY_, conf_lvl = _CONFIDENCELEVEL_)
```

Note: For this code to work the explanatory variable must only have two categories.


## Chapter 8: Hypothesis Testing Means

### Paired $\mathrm{T}$-Test and Confidence Interval

Note: Confidence levels default to 95% but can be overridden with `conf_lvl = _DECIMAL_` (e.g., `conf_lvl = 0.90`). 

```{verbatim, lang = "r"}
infer_paired(_DATANAME_, var1 = ~_VARIABLE1_, var2 = ~_VARIABLE2_, conf_lvl = _CONFIDENCELEVEL_)
```

Use the `mu0` argument to specify the value of the null hypothesis, if different from 0. E.g., `mu0 = 3`.

### Independent $\mathrm{T}$-Test

```{verbatim, lang = "r"}
infer_2mean_test(_DATANAME_, _VARIABLE_~_GROUPVARIABLE_)
```

Use the `null` argument to specify the value of the null hypothesis, if different from 0. E.g., `null = 3`.

### Independent 2 Groups Confidence Interval

```{verbatim, lang = "r"}
infer_2mean_int(_DATANAME_, _VARIABLE_~_GROUPVARIABLE_, conf_lvl = _CONFIDENCELEVEL_)
```

### ANOVA

```{verbatim, lang = "r"}
infer_anova(_DATANAME_, _VARIABLE_~_GROUPVARIABLE_)
```

# Optional Functions / Topics

## Hypothesis Test on $p$

```{verbatim, lang = "r"}
infer_1prop_test(_DATANAME_, ~_VARIABLE_, success = "_SUCCESSCATEGORY_", p0 = _NULL_)
```

Use the `p0` argument to specify the value of the null hypothesis, if different from 0.5. E.g., `p0 = 0.3`.

## Hypothesis Test on &mu;

```{verbatim, lang = "r"}
infer_1mean_test(_DATANAME_, ~_VARIABLE_, mu0 = _NULL_)
```

Use the `mu0` argument to specify the value of the null hypothesis, if different from 0. E.g., `p0 = 3`.
